Individual heterogeneity in the functional network topography of the medial prefrontal cortex

### 2019-05-03 Manuscript.Rmd
new citations + new discussion paragraph

  However, strong conclusions about functional colocalization require consideration of individual-level heterogeneity in topographic patterns of brain activity. A recognized limitation of group averaging and meta-analysis is that individual-specific functional subdivisions can be blurred and overlooked [@Fedorenko2012; @Michalka2015; @Tobyne2018; @Wang2015; @Woo2014], potentially exaggerating the degree of overlap across domains. This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013a]. An alternative approach is to focus on analyses at the individual-participant level. Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Gordon2017; @Gratton2018b; @Laumann2015; @Tobyne2018]. Subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018]. Recent work has uncovered fine-grained subdivisions within the DN using both data-driven clustering and individually customized seed-based connectivity analysis [@Braga2017; @Braga2019]. It is therefore possible that the diffuse overlap of DN and valuation effects can be attributed to low effective spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level. An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DN effects within mPFC and PCC.

@@

However, the interpretation of overlap in group-level data depends on the degree to which functional organization is heterogeneous across individuals. Recent studies have shown that heteromodal brain regions have considerable variability in functional connectivity across individuals [@Muller2013], individual-specific functional topography can be occluded in aggregative estimations [@Braga2017; @Gordon2017; @Michalka2015; @Tobyne2018], and overlap in functional activation can vanish with increases in spatial precision [@Woo2014]. These findings suggest that group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains. However, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive so far. Therefore, affirming that among DN and valuation share neural substrates in this area first requires: 1) a method to reliably and precisely capture its functional topography in isolated individuals; and 2) quantifying the degree of heterogeneity of its intrinsic functional organization in a large group of individuals.

@@

Our results are complementary with previous studies that described individual-specific brain organization using a different data aspect ratio [fewer individuals and more data per individual; Gordon, Braga, Poldrack]. While inter-individual differences in functional topography have been described in these studies, here we were able to quantify the variability in a large sample. and our method does not require massively multi-session data acquisition.

@@

And write a portion on the lack of subcortical reward-related regions (i.e. striatum). Say something like 'incorporating the ventral striatum did not refine these partitions through either method. This could be due to the lack of signal modulation of this area at rest, and should be examined through behavioral manipulations of value in the future. Instead, here we focus on capturing the intrinsic functional heterogeneity of mPFC as a way to pave the path to refined analyses aimed at disentangling DN and SV'. It is worth noting that the SV-only area from the meta-analysis tends to land in non-DN, although it ends up in no-ones land when thresholding the maps.

It might also be worth mentioning that previous work has established the shift in network types during rest through hidden Markov models (Vidaurre et al., 2016?). While this suggests that we should see fluctuations in affiliation, and not stability, Vidaurre's work establishes the dynamics of prevalent function among networks, and not their topologies. Our work focuses on the topographical arrangement of the DN network, which can be active or not while maintaining its form. So, the two works are compatible. Note, I played a bit with AR and MA processes per subject to try to understand the autocorrelation in the sliding window. First, both acf/pacf and arima (order = n,0,n) R functions suggested that the data was better fit by AR. Moreover, ARs from 1 to 10 had neglegible differences, so I stuck with 1 results for simplicity. As expected the data is significantly autocorrelated, and when I checked plotted the residuals they were mostly within the 0.15 bound (normally distributed). Coefficients ranged from 0.6 to 1. So, there is clear rythmicity in the agreement between each window and the overall pattern. However, the intercepts from the ARn processes gave more or less the same estimates as the mean rand index over all the windows. This is mostly expected, as we saw that the standard deviation of the rand index was low across participants. I am currently interpreting this as a signal that there is clear periodicity that is otherwise harmless for our results: in the end, the agreement remains stable throughout the 4800 TRs.

In terms of noise, there are a handful of things to keep in mind. First is that yes, mPFC is noisier overall, but that did not preclude the relatively high levels of agreement across days and sessions per subject, even though ARI heavily penalizes discrepancies (less than linearly). Second, low $R^2$ values were found all throughout the z-axis, meaning that variance explained is not strictly determined by the cardinal position of the vertex (and while the correlation was significant due to the sheer number of items, the coefficient was relatively low). Right now this might be ok as a way to bypass noise comments, but it would also be interesting to take advantage of the Fiedler vector here. Since it's linearly related to $R^2$ per subject, perhaps finding a way to threshold these values would provide cleaner and even more consistent maps.

So what's the advantage of this work over previous ones? Gratton, Gordon, and Kong have already found some degree of subject stability and intersubject variability. Ours complements these findings by looking at the vertex level, not just mean parcel activity (this made sense for them, as they were looking at the whole brain). Also, most of these analyses rely on a small set of oversampled subjects (i.e. MSC). Here we extend this to 100, giving credit to individualize examinations even without oversampling.

>>>>

  However, strong conclusions about functional colocalization require consideration of individual-level heterogeneity in topographic patterns of brain activity. A recognized limitation of group averaging and meta-analysis is that individual-specific functional subdivisions can be blurred and overlooked [@Fedorenko2012; @Michalka2015; @Tobyne2018; @Wang2015; @Woo2014], potentially exaggerating the degree of overlap across domains. This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013]. An alternative approach is to focus on analyses at the individual-participant level. Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Gordon2017; @Gratton2018b; @Laumann2015; @Tobyne2018]. Subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018]. Recent work has uncovered fine-grained subdivisions within the DN using both data-driven clustering and individually customized seed-based connectivity analysis [@Braga2017; @Braga2019]. It is therefore possible that the diffuse overlap of DN and valuation effects can be attributed to low effective spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level. An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DN effects within mPFC and PCC.

@@

However, the interpretation of overlap in group-level data depends on the degree to which functional organization is heterogeneous across individuals. Recent studies have shown that heteromodal brain regions have considerable variability in functional connectivity across individuals [@Mueller2013], individual-specific functional topography can be occluded in aggregative estimations [@Braga2017; @Gordon2017; @Michalka2015; @Tobyne2018], and overlap in functional activation can vanish with increases in spatial precision [@Woo2014]. These findings suggest that group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains. However, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive so far. Therefore, affirming that among DN and valuation share neural substrates in this area first requires: 1) a method to reliably and precisely capture its functional topography in isolated individuals; and 2) quantifying the degree of heterogeneity of its intrinsic functional organization in a large group of individuals.

@@

Our results are complementary with previous studies that described individual-specific brain organization. On one hand, topographical heterogeneity has been qulitatively highlighted using a different data aspect ratio [few individuals and more data per individual; @Gordon2017, @Braga2017, @Braga2019]. In terms of stability, previous work has relied on parcellations and group priors to show that an individual's functional connectivity pattern is consistent in time [@Gratton2018; @Kong2018], thus being relatively insensitive to an individual's complex topography. Here we were able to quantify the variability and stability of fine-scale functional topography in a large sample with moderately low amounts of data (down to a single 15 minute scan).

@@

And write a portion on the lack of subcortical reward-related regions (i.e. striatum).
